Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-22 R0V0.tex
Change the proof Proposition 1 to explain the dependence of F on nodes x_i, \breve{x_i}, \hat{x}_i. Change the times on the tables for the examples

\mypara For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem to satisfy the set of equations~\eqref{eq:main result}. This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}. In particular, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be done in parallel. To that end chordal graphs are employed. It utilizes the network topology to decompose it into smaller complete components.

\begin{proposition}\label{prop:clique tree decomposition}
	Let $p\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $p$ matrix inequalities with smaller dimension. Moreover, if each matrix is negative definite, then the MI~\eqref{eq:MI:SSCCM} is satisfied.
\end{proposition}

\begin{proof}
	Using the Algorithm~3.1 from \cite{VandenbergheAndersen2015}, it is possible to decompose the graph $\mathscr{G}$ into the clique tree $\mathscr{T}(\mathscr{G})$. Let the integer $p>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$. The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.

\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_p$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}_k$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,p]}$. For each index $k\in\mathbb{N}_{[1,p]}$, define the matrix $E_k\in\mathbb{R}^{\dim_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.

\mypara    Denote the left-hand side of the MI~\eqref{eq:MI:SSCCM} by $T$. The existence of $p$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\mathbin{\mathtt{card}}_k}\to\mathbb{R}^{\mathbin{\mathtt{card}}_k\times \mathbin{\mathtt{card}}_k}$, where $k\in\mathbb{N}_{[1,p]}$, satisfying the equation
   \begin{equation*}
   	 T=\sum_{k=1}^p E_k^\top F_k E_k\;.
  	\end{equation*}

\mypara Consequently, whenever the following matrix inequality holds 
  	\begin{equation}\label{eq:MIF}
  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,p]},
	\end{equation}
	uniformly over $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI:SSCCM} holds. This concludes the proof.
\end{proof}

@@

\mypara To show the advantages of the method proposed in this paper, a benchmark composed of  three scenarios, according to the constraints imposed on the matrix $Y$, has been created.  Namely, the unconstrained case, the ``neighbor'' case, and the fully decentralized case. For the two latter cases, it was possible to consider up to $N=256$ systems for the ``neighbor'' case and up to $N=512$ systems for the fully decentralized (diagonal) case. In these scenarios the techniques provided by chordal graphs have been employed.

@@

\mypara The solver took 98  seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has elements defined, for every $q\in\mathbb{R}^8$, by
\begin{align*}
	\overline{Y}_i(q)=&-2\begin{bmatrix}
	y_i&1+\sum_{k=1}^4 y_k^2+x_k^2
	\end{bmatrix},\\
	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},\\
	0_{1\times2}=&\begin{bmatrix}0,&0\end{bmatrix},
\end{align*}
where $i\in\mathbb{N}_{[1,4]}$, and structure given by the matrix
\begin{equation}\label{eq:example:Y:general}
		\resizebox*{0.85\columnwidth}{!}{$\begin{bmatrix}
			\overline{Y}_1(q),&0_{1\times 2},&-0.03\hat{Y}_1(q),&0_{1\times2}\\
			0_{1\times 2},&\overline{Y}_2(q),&0_{1\times 2},&-0.04\hat{Y}_2(q)\\
			-0.04\hat{Y}_3(q),&0_{1\times 2},&\overline{Y}_3(q),&0_{1\times 2}\\
			0_{1\times 2},&-0.03\hat{Y}_4(q),&0_{1\times 2},&\overline{Y}_4(q)
		\end{bmatrix}$}.
\end{equation}

@@

\mypara The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result}, in this case, was 3.5 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
\begin{equation}\label{eq:example:Y:neighbor and decentralized}
	 Y(q)=\begin{bmatrix}
 	\overline{Y}_1(\cdot)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&\overline{Y}_2(\cdot)&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&\overline{Y}_3(\cdot)&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_4(\cdot)
 \end{bmatrix}\;,
\end{equation}
with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
\begin{equation*}
	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}, i\in\mathbb{N}_{[1,4]}\;.
\end{equation*}

\mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$. The time taken by the parser to solve the set of matrix inequalities~\eqref{eq:main result} was 4.4 seconds, the matrix $W$ is given by
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
\end{align*}

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}\vspace{-2em}
	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (8 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&98s\\
	Neighbor&3.5s\\
	Fully decentralized&4.4s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
	\label{tab:chain case}
\end{table}

@@

\mypara The solver took 48s to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ obtained is given by
\begin{equation*}
	W=\mathbin{\mathtt{diag}}(0.1,1,0.1,1,0.1,1,0.1,1,0.1,1,0.3,1).
\end{equation*}
The matrix $Y$ is given by
\begin{equation*}
	\begin{bmatrix}
		\overline{Y}_{11}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&\underline{Y}_{22}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&\overline{Y}_{33}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{44}(q)&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{55}(q)&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\underline{Y}_{66}(q)
	\end{bmatrix},
\end{equation*}
for every $q\in\mathbb{R}^{12}$, where 
\begin{align*}
 \overline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&4+4\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},\\
 \underline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&2+2\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},
\end{align*}
for each index $i,j\in\mathbb{N}_{[1,6]}$.

\mypara In the ``neighbor'' case, the topology of the controller is the same as of the network. More precisely, $\mathscr{G}_c=\mathscr{G}_p$. The solver took 57s to solve the set of matrix inequalities~\eqref{eq:main result}.

@@

\mypara In the last scenario, the fully decentralized case, the set of edges $\mathscr{E}_c$ of the graph $\mathscr{G}_c$ is specified as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$ and no constrained were imposed on the matrix $Y$. The solver took 43s to solve the set of matrix inequalities~\eqref{eq:main result}.

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&48s\\
	Neighbor&57s\\
	Fully decentralized&43s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
	\label{tab:mixed example}
\end{table}

>>>>

\mypara For large scale systems, the dimension of the matrices $W$ and $Y$ can be a problem to satisfy the set of equations~\eqref{eq:main result}. This is due to the fact that semidefinite programming become less efficient when those matrices have high rank \cite{VandenbergheBoyd1996}. Thus, the computation of a solution to MI~\eqref{eq:MI:SSCCM} need to be scalable, in the sense that adding more agents to the network will make the time taken to compute the controller linearly. To that end chordal graphs are employed to decompose the network topology into smaller complete components.

\begin{proposition}\label{prop:clique tree decomposition}
	Let $\mathscr{G}:=\mathscr{G}_p\cup\mathscr{G}_c$ and $l\in\mathbb{N}_{>0}$ be the number of nodes of the clique tree $\mathscr{T}(\mathscr{G})$. Then, the MI~\eqref{eq:MI:SSCCM} can be decomposed into $p$ matrix inequalities with smaller dimension. Moreover, if each matrix is negative definite, then the MI~\eqref{eq:MI:SSCCM} is satisfied.
\end{proposition}

\begin{proof}
	Using the Algorithm~3.1 from \cite{VandenbergheAndersen2015}, it is possible to decompose the graph $\mathscr{G}$ into the clique tree $\mathscr{T}(\mathscr{G})$. Let the integer $l>0$ be the number of nodes of $\mathscr{T}(\mathscr{G})$. The remainder of this proof is based on Section~II of \cite{PakazadHanssonAndersenEtAl2015}.

\mypara 	Let the sets $\mathscr{C}_1,\ldots,\mathscr{C}_l$ be the nodes of $\mathscr{T}(\mathscr{G})$, and $\mathbin{\mathtt{card}}_k$ be cardinality (number of elements) of the set $\mathscr{C}_k$, $k\in\mathbb{N}_{[1,l]}$. For each index $k\in\mathbb{N}_{[1,l]}$, define the matrix $E_k\in\mathbb{R}^{\mathbin{\mathtt{card}}_k\times n}$ obtained from the $n\times n$ identity matrix with blocks of rows indexed by $\mathbb{N}_{[1,N]}\setminus \mathscr{C}_k$ removed.

\mypara    Denote the left-hand side of the MI~\eqref{eq:MI:SSCCM} by $T$. The existence of $l$ cliques implies that there exist matrices $F_k:\mathbb{R}^{\mathbin{\mathtt{card}}_k}\to\mathbb{R}^{\mathbin{\mathtt{card}}_k\times \mathbin{\mathtt{card}}_k}$, where $k\in\mathbb{N}_{[1,l]}$, satisfying the equation
   \begin{equation*}
   	 T=\sum_{k=1}^p E_k^\top F_k E_k\;.
  	\end{equation*}

\mypara Without loss of generality, assume that the node $i\in\mathscr{V}_c$ is contained in the clique $\mathscr{C}_k$. Whenever the following matrix inequality 
  	\begin{equation}\label{eq:MIF}
  		F_k\prec0,\quad\forall k\in\mathbb{N}_{[1,l]},
	\end{equation}
	holds uniformly, the matrix $T$ is uniformly negative definite. Thus, the MI~\eqref{eq:MI:SSCCM} holds.

	For each node $i\in\mathscr{V}_p\cup\mathscr{V}_c$ contained in the clique $\mathscr{C}_k$. The corresponding matrix $F_k$ has arguments $x_i, \breve{x}_i$ and $\vec{x}_i$. In other words, $F_k$ depends on how strongly the nodes of the of the system (defined by $\mathscr{G}_c$) and communication network (defined by $\mathscr{G}_p$) are connected among each other. This concludes the proof.
\end{proof}

@@

\mypara To show the advantages of the method proposed in this paper, a benchmark composed of  three scenarios, according to the constraints imposed on the matrix $Y$, has been created.  Namely, the unconstrained case, the ``neighbor'' case, and the fully decentralized case. For the two latter cases, it was possible to consider up to $N=512$ systems. In these scenarios the techniques provided by chordal graphs have been employed.

@@

\mypara The solver took 31 seconds to compute a solution to the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has elements defined, for every $q\in\mathbb{R}^8$, by
\begin{align*}
	\overline{Y}_i(q)=&-2\begin{bmatrix}
	y_i&1+\sum_{k=1}^4 y_k^2+x_k^2
	\end{bmatrix},\\
	\hat{Y}_i(q)=&-\begin{bmatrix}y_i,&0\end{bmatrix},\\
	0_{1\times2}=&\begin{bmatrix}0,&0\end{bmatrix},
\end{align*}
where $i\in\mathbb{N}_{[1,4]}$, and structure given by the matrix
\begin{equation}\label{eq:example:Y:general}
		\resizebox*{0.85\columnwidth}{!}{$\begin{bmatrix}
			\overline{Y}_1(q),&0_{1\times 2},&-0.03\hat{Y}_1(q),&0_{1\times2}\\
			0_{1\times 2},&\overline{Y}_2(q),&0_{1\times 2},&-0.04\hat{Y}_2(q)\\
			-0.04\hat{Y}_3(q),&0_{1\times 2},&\overline{Y}_3(q),&0_{1\times 2}\\
			0_{1\times 2},&-0.03\hat{Y}_4(q),&0_{1\times 2},&\overline{Y}_4(q)
		\end{bmatrix}$}.
\end{equation}

@@

\mypara The time taken by solver to find a solution to the set of matrix inequalities~\eqref{eq:main result}, in this case, was 3 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure defined, over $q\in\mathbb{R}^8$ as
\begin{equation}\label{eq:example:Y:neighbor and decentralized}
	 Y(q)=\begin{bmatrix}
 	\overline{Y}_1(\cdot)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&\overline{Y}_2(\cdot)&0_{1\times2}&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&\overline{Y}_3(\cdot)&0_{1\times2}\\
 	0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_4(\cdot)
 \end{bmatrix}\;,
\end{equation}
with elements given, for every $(q_i,\breve{q}_i)\in\mathbb{R}^2\times\mathbb{R}^{\breve{n}_i}$, by 
\begin{equation*}
	\overline{Y}_i(q_i,\breve{q}_i)=-2\begin{bmatrix}
	y_i,&1+\sum_{j\in\mathscr{N}(i)}x_j^2+y_j^2)\end{bmatrix}, i\in\mathbb{N}_{[1,4]}\;.
\end{equation*}

\mypara In the fully decentralized case, the set of edges $\mathscr{E}_c$ is defined as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$. The time taken by the solver to find a solution to the set of matrix inequalities~\eqref{eq:main result} was 2.5 seconds, the matrix $W$ is given by
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
\end{equation*}
and the matrix $Y$ with structure given by \eqref{eq:example:Y:neighbor and decentralized} with elements defined, for every $q_i\in\mathbb{R}^2$, by 
\begin{align*}
 \overline{Y}_i(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix},\quad i\in\mathbb{N}_{[1,4]}\;.
\end{align*}

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}\vspace{-2em}
	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (8 for the unconstrained case, 512 for the other cases). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&31s\\
	Neighbor&3s\\
	Fully decentralized&2.5s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:graph}.}
	\label{tab:chain case}
\end{table}

@@

\mypara The solver took 32s to solve the set of matrix inequalities~\eqref{eq:main result}. The matrix $W$ obtained is given by
\begin{equation*}
	W=\mathbin{\mathtt{diag}}(0.1,1,0.1,1,0.1,1,0.1,1,0.1,1,0.3,1).
\end{equation*}
The matrix $Y$ is given by
\begin{equation*}
	\begin{bmatrix}
		\overline{Y}_{11}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&\underline{Y}_{22}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&\overline{Y}_{33}(q)&0_{1\times2}&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{44}(q)&0_{1\times2}&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\overline{Y}_{55}(q)&0_{1\times2}\\
		0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&0_{1\times2}&\underline{Y}_{66}(q)
	\end{bmatrix},
\end{equation*}
for every $q\in\mathbb{R}^{12}$, where 
\begin{align*}
 \overline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&4+4\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},\\
 \underline{Y}_{ij}(q)=&\ -\begin{bmatrix}3y_i,&2+2\sum_{i=1}^6(x_i^2+y_i^2)\end{bmatrix},
\end{align*}
for each index $i,j\in\mathbb{N}_{[1,6]}$.

\mypara In the ``neighbor'' case, the topology of the controller is the same as of the network. More precisely, $\mathscr{G}_c=\mathscr{G}_p$. The solver took 17s to solve the set of matrix inequalities~\eqref{eq:main result}.

@@

\mypara In the last scenario, the fully decentralized case, the set of edges $\mathscr{E}_c$ of the graph $\mathscr{G}_c$ is specified as $\mathscr{E}_c=\{(1,1),(2,2),(3,3),(4,4)\}$ and no constrained were imposed on the matrix $Y$. The solver took 12s to solve the set of matrix inequalities~\eqref{eq:main result}.

@@

\begin{table}
	\begin{tabular}{r|c}
	Case&Time taken by the solver (4 agents)\\ \hline
	Unconstrained&32s\\
	Neighbor&17s\\
	Fully decentralized&12s\\\hline
	\end{tabular}\vspace{1em}
	\caption{A summary of the time taken to solve the set of matrix inequalities~\eqref{eq:main result} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
	\label{tab:mixed example}
\end{table}
